---
title: "Paper Visuals"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(jpeg)
library(png)
library(grid)
library(ggplot2)
```

# Shooting Component
## Curry James Barchart
```{r}
curryjames <- as.data.frame(shootingdata %>% filter(namePlayer %in% c("Stephen Curry", "LeBron James") & slugSeason == "2018-19") %>% group_by(namePlayer) %>% summarise(count=n(), three = sum(zoneBasic %in% c("Above the Break 3", "Left Corner 3", "Right Corner 3", "Backcourt")), paint = sum(zoneBasic %in% c("In The Paint (Non-RA)", "Restricted Area"))) %>% mutate(paint_prop = paint / count, three_prop = three / count))
  
curryjames <- gather(curryjames, event, total, paint_prop:three_prop)
curryjames %>% ggplot(aes(namePlayer, total, fill=event)) + geom_bar(stat = "identity", position = 'dodge') + ggtitle("Where Curry and James Get Shots From") + xlab("") + ylab("Proportion") + scale_fill_manual(name = "Location", labels = c("Paint", "Three"), values = c("#ADD8E6", "#E8ADAA")) + theme_classic() + theme(plot.title = element_text(hjust = 0.5))

```

# Getting dataframe of average shooting distance for each player:
```{r}
shotdistance <- function(id, season){
  playername <- idtoname(id)
  height <- as.integer(myrosters %>% filter(idPlayer == id & slugSeason == season) %>% summarise(height=heightInches))
  shotdistance <- as.numeric(shootingdata %>% filter(idPlayer==id & slugSeason==season) %>% summarise(dist = mean(distanceShot)))
  playerdf <- as.data.frame(cbind(playername, id, season, height, shotdistance))
  colnames(playerdf) <- c("playerName", "playerId", "slugSeason", "heightInches", "shotDistance")
  return(playerdf)
}

rosters201819 <- myrosters %>% filter(slugSeason == "2018-19")
for(i in 1:nrow(rosters201819)){
  if(i==1){
    distance <- shotdistance(rosters201819[i,14], rosters201819[i,1])
  } else{
    helper <- shotdistance(rosters201819[i,14], rosters201819[i,1])
    distance <- rbind(distance, helper)
  }
  i = i + 1
}

```

# LeBron shooting chart 2018-19
```{r}
leBron <- shootingdata %>% filter(namePlayer == "LeBron James" & slugSeason == "2018-19")
picture <- readPNG("/Users/patricksimpson/Desktop/NBAHC/Visuals/Paper/LeBron1819.png", native = FALSE)
picture <- rasterGrob(picture, width = unit(1,"npc"), height = unit(1,"npc"))

court <- readJPEG("/Users/patricksimpson/Desktop/NBAHC/Visuals/nba_court.jpg")
court <- rasterGrob(court, width = unit(1,"npc"), height = unit(1,"npc"))

ggplot(leBron, aes(x=locationX, y=locationY)) + annotation_custom(court, -250, 250, -52, 420) +geom_point(aes(colour = typeEvent, alpha = 0.1)) + scale_color_manual(values = c("#FF0000", "#ADD8E6")) + xlim(-225,225) + ylim(-30, 397) + annotation_custom(picture, 145, 245, 310, 410) + theme(plot.title = element_text(hjust = 0.5),axis.ticks.x=element_blank(), axis.text.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank(), legend.position = "none") + xlab("") + ylab("")

```

# Curry shot chart 2018-19:
```{r}
Curry <- shootingdata %>% filter(namePlayer == "Stephen Curry" & slugSeason == "2018-19")
picture <- readPNG("/Users/patricksimpson/Desktop/NBAHC/Visuals/Paper/Curry1819.png", native = FALSE)
picture <- rasterGrob(picture, width = unit(1,"npc"), height = unit(1,"npc"))

court <- readJPEG("/Users/patricksimpson/Desktop/NBAHC/Visuals/nba_court.jpg")
court <- rasterGrob(court, width = unit(1,"npc"), height = unit(1,"npc"))

ggplot(Curry, aes(x=locationX, y=locationY)) + annotation_custom(court, -250, 250, -52, 420) +geom_point(aes(colour = typeEvent, alpha = 0.1)) + scale_color_manual(values = c("#FF0000", "#ADD8E6")) + xlim(-225,225) + ylim(-30, 397) + annotation_custom(picture, 145, 245, 310, 410) + theme(plot.title = element_text(hjust = 0.5), axis.ticks.x=element_blank(), axis.text.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank(), legend.position = "none") + xlab("") + ylab("")

```

# 3PT shooting proportion by season:
```{r}
shootingdata %>% filter(slugSeason %in% c("2014-15", "2015-16", "2016-17", "2017-18", "2018-19")) %>% group_by(slugSeason) %>% summarise(totalShots = n(), threes = sum(zoneBasic %in% c("Above the Break 3", "Left Corner 3", "Right Corner 3", "Backcourt"))) %>% mutate(prop = threes / totalShots) %>% ggplot(aes(slugSeason, prop)) + geom_col() + ylab("Proportion of 3PT Attempts") + xlab("Season") + ggtitle("Proportion of 3PT Field Goals vs. Season") + theme_classic() + theme(plot.title = element_text(hjust = 0.5)) + geom_text(aes(label=round(prop, 4)), position=position_dodge(width=0.9), vjust=-0.25) + scale_fill_manual(values = c("#B6B6B4", "#B6B6B4", "#B6B6B4","#B6B6B4","#B6B6B4"))

```

# Results from shooting component:
```{r}
library(magrittr) # Allows me to change colnames when piping
library(xtable) # To transfer table to latex

shootingcomp <- read.csv("/Users/patricksimpson/Desktop/NBAHC/Shooting/test.csv")
shootingcomp <- shootingcomp %>% filter(gamesPlayed > 15 & FG3A > 50)
x <- reactable(shootingcomp[order(-shootingcomp$adjustment),] %>% head() %>% select(namePlayer, Season, FG3A, adjustment) %>% set_colnames(c("Player", "Season", "FG3A", "Component")))
```

# Mid-Range Decline:
```{r}
shootingdata %>% filter(slugSeason %in% c("2014-15", "2015-16", "2016-17", "2017-18", "2018-19")) %>% group_by(slugSeason) %>% summarise(totalShots = n(), mr = sum(zoneBasic %in% c("Mid-Range"))) %>% mutate(prop = mr / totalShots) %>% ggplot(aes(slugSeason, prop)) + geom_col() + ylab("Proportion of Mid-Range Attempts") + xlab("Season") + ggtitle("Proportion of Mid-Range Field Goal Attempts vs. Season") + theme_classic() + theme(plot.title = element_text(hjust = 0.5)) + geom_text(aes(label=round(prop, 4)), position=position_dodge(width=0.9), vjust=-0.25) + scale_fill_manual(values = c("#B6B6B4", "#B6B6B4", "#B6B6B4","#B6B6B4","#B6B6B4"))
```

# Mid-Range By Quarter:
```{r}
shootingdata %>% filter(slugSeason %in% c("2014-15", "2015-16", "2016-17", "2017-18", "2018-19")) %>% filter(zoneBasic == "Mid-Range") %>% group_by(slugSeason) %>% summarise(totalshots = n(),q1 = sum(numberPeriod==1), q2 = sum(numberPeriod==2), q3 = sum(numberPeriod==3), q4 = sum(numberPeriod==4), q5 = sum(numberPeriod==5))



```

```{r}

shootingdata %>% filter(slugSeason %in% c("2014-15", "2015-16", "2016-17", "2017-18", "2018-19")) %>% filter(numberPeriod==4) %>% group_by(slugSeason) %>% summarise(totalshots=n(), mr=sum(zoneBasic=="Mid-Range"), three = sum(zoneBasic %in% c("Above the Break 3", "Left Corner 3", "Right Corner 3")), paint=sum(zoneBasic %in% c("In The Paint (Non-RA)", "Restricted Area"))) %>% mutate(mr_prop = mr/totalshots)

```


# Inside Scoring Proportion of attempts by Season
```{r}
shootingdata %>% filter(slugSeason %in% c("2014-15", "2015-16", "2016-17", "2017-18", "2018-19")) %>% group_by(slugSeason) %>% summarise(totalShots = n(), threes = sum(zoneBasic %in% c("In The Paint - (Non-RA)", "Restricted Area"))) %>% mutate(prop = threes / totalShots) %>% ggplot(aes(slugSeason, prop)) + geom_col() + ylab("Proportion") + xlab("Season") + ggtitle("Proportion of Paint Attempts vs. Season") + theme_classic() + theme(plot.title = element_text(hjust = 0.5)) + geom_text(aes(label=round(prop, 4)), position=position_dodge(width=0.9), vjust=-0.25) + scale_fill_manual(values = c("#B6B6B4", "#B6B6B4", "#B6B6B4","#B6B6B4","#B6B6B4"))

```

# Efficiency based upon shot location:
```{r}
#shootingdata %>% filter(slugSeason %in% c("2014-15", "2015-16", "2016-17", "2017-18", "2018-19")) %>% group_by(zoneBasic) %>% summarise(made_shots = sum(isShotMade == TRUE), count = n()) %>% mutate(fgp = made_shots / count) %>% filter(zoneBasic != "Backcourt") %>% ggplot(aes(zoneBasic, fgp)) + geom_col() + ylab("Field Goal Percentage") + xlab("Shot Location") + ggtitle("Field Goal Percentage by Shot Location over last 5 Seasons") + theme_classic() + theme(plot.title = element_text(hjust = 0.5)) + geom_text(aes(label=round(fgp, 4)), position=position_dodge(width=0.9), vjust=-0.25) + scale_fill_manual(values = c("#B6B6B4", "#B6B6B4", "#B6B6B4","#B6B6B4","#B6B6B4"))

Loc <- as.data.frame(c("Three", "Mid-Range", "Paint"))
Made <- as.data.frame(c(87183+15494+14827, 90070, 63898+209244))
Attempted <- as.data.frame(c(249241+40550+38198, 225095, 158929+340168))
x <- cbind(Loc, Made, Attempted)
colnames(x) <- c("Location", "Made_shots", "FGA")
x <- x %>% mutate(fgp = Made_shots / FGA, ppp = ifelse(Location %in% c("Three"), fgp*3, fgp*2))

x1 <- gather(x, event, total, fgp:ppp)
x1 %>% ggplot(aes(Location, total, fill=event)) + geom_bar(stat = "identity", position = 'dodge') + ggtitle("FGP and PPP Based on Shot Location (2013-19)") + xlab("") + ylab("") + theme_classic() + theme(plot.title = element_text(hjust = 0.5)) + geom_text(aes(label=round(total, 4)),position=position_dodge(width=0.9), vjust=-0.25) + scale_fill_manual(name = "", labels = c("FGP", "PPP"), values = c("#ADD8E6", "#E8ADAA"))

```

# Proportion of pick and rolls:
```{r}
#library(gghighlight)

#gghighlight_line(d, aes(idx, value, colour = type), predicate = max(value) > 20)

#y<- synergyoffense %>% group_by(Season, PlayType) %>% summarise(count = sum(poss)) %>% mutate(tot = sum())
#write.csv(y, "/Users/patricksimpson/Desktop/syn.csv", row.names = FALSE)
#y <- read.csv("/Users/patricksimpson/Desktop/syn.csv")
#y$Season <- as.factor(y$Season)
y %>% ggplot(aes(Season2, prop, colour = PlayType)) + geom_line() + xlab("Season") + ylab("Proportion") + ggtitle("Halfcourt Offenses Over Last 4 Seasons") + theme_linedraw() + theme(plot.title = element_text(hjust = 0.5), panel.grid.major.x = element_blank())


```

# Pick and Roll Diagram
```{r}

ggplot(data, aes(x=V1, y=V2)) + annotation_custom(court, -250, 250, -52, 420) + xlim(-228,228) + ylim(-32, 402) + xlab("") + ylab("") + theme(axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank()) + annotate("text", x = 20, y = 260, label = "5", fontface = 2, size = 6, colour = "blue") + annotate("text", x = 0, y = 300, label = "1", fontface = 2, size = 6, colour = "blue") + annotate("text", x = 225, y = 5, label = "2", fontface = 2, size = 6, colour = "blue") + annotate("text", x = -225, y = 5, label = "4", fontface = 2, size = 6, colour = "blue") + annotate("text", x = -190, y = 200, label = "3", fontface = 2, size = 6, colour = "blue") + annotate("text", x = 0, y = 260, label = "A", fontface = 2, size = 6, colour = "red") + annotate("text", x = -175, y = 180, label = "C", fontface = 2, size = 6, colour = "red") + annotate("text", x = -200, y = 5, label = "D", fontface = 2, size = 6, colour = "red") + annotate("text", x = 200, y = 5, label = "B", fontface = 2, size = 6, colour = "red") + annotate("text", x = 20, y = 215, label = "E", fontface = 2, size = 6, colour = "red")
```


# Playmaking:
```{r}
#dribdefense %>% group_by(rangeDribble) %>% summarise(attempts = sum(fga), makes = sum(fgm)) %>% mutate(prop = attempts / sum(attempts), percentage = makes / attempts) %>% mutate(x = ifelse(rangeDribble %in% c("0 Dribbles", "1 Dribble"), "Assisted", "Unassisted"))

#z<- as.data.frame(cbind(c("Assisted", "Unassisted"), c(0.4814128 + 0.1354275, 1-0.4814128-0.1354275), c((280402+79024) / (575129+161791), (61978+95411+54336) / (132629+205488+119632))))
colnames(z) <- c("Type", "prop", "fgp")

z$prop <- as.numeric(as.character(z$prop))
z %>% ggplot(aes(Type, prop)) + geom_bar(stat = "identity", position = 'dodge') + ggtitle("Proportion of Assisted vs. Unassisted Attempts (2013-19)") + xlab("") + ylab("") + theme_classic() + theme(plot.title = element_text(hjust = 0.5)) + geom_text(aes(label=round(prop, 4)),position=position_dodge(width=0.9), vjust=-0.25) + scale_fill_manual(name = "", labels = c("FGP", "PPP"), values = c("#000000", "#C0C0C0"))

#z1 <- gather(z, event, total, prop:fgp)
z1$total <- as.numeric(as.character(z1$total))

z1 %>% ggplot(aes(Type, total, fill=event)) + geom_bar(stat = "identity", position = 'dodge') + ggtitle("Assisted vs. Unassisted FGP and Proportion of Shot Attempts (2013-19)") + xlab("") + ylab("") + theme_classic() + theme(plot.title = element_text(hjust = 0.5)) + geom_text(aes(label=round(total, 4)),position=position_dodge(width=0.9), vjust=-0.25) + scale_fill_manual(name = "", labels = c("FGP", "Prop"),values = c("#ADD8E6", "#E8ADAA"))


#x1 <- gather(x, event, total, fgp:ppp)
#x1 %>% ggplot(aes(Location, total, fill=event)) + geom_bar(stat = "identity", position = 'dodge') + ggtitle("FGP and PPP Based on Shot Location (2013-19)") + xlab("") + ylab("") + theme_classic() + theme(plot.title = element_text(hjust = 0.5)) + geom_text(aes(label=round(total, 4)),position=position_dodge(width=0.9), vjust=-0.25) + scale_fill_manual(name = "", labels = c("FGP", "PPP"), values = c("#000000", "#C0C0C0"))

```

# Isolation:
```{r}
dribdefense %>% group_by(rangeDribble) %>% summarise(made = sum(fgm), att = sum(fga)) %>% mutate(fgp = made/att) %>% ggplot(aes(rangeDribble, fgp)) + geom_bar(stat = "identity", position = 'dodge') + ggtitle("Assisted vs. Unassisted FGP and Proportion of Shot Attempts (2013-19)") + xlab("") + ylab("") + theme_classic() + theme(plot.title = element_text(hjust = 0.5)) + geom_text(aes(label=round(fgp, 4)),position=position_dodge(width=0.9), vjust=-0.25)

dribdefense %>% group_by(rangeDribble) %>% summarise(made3 = sum(fg3m), att3 = sum(fg3a)) %>% mutate(fg3p = made3 / att3)
```

# Defense
```{r}

teamstats %>% group_by(Season,Postseason) %>% summarise(avg = mean(Adjusted.DRtg.A)) %>% ggplot(aes(Season, avg, fill=Postseason)) + geom_bar(stat = "identity", position = 'dodge') + ggtitle("Adjusted Defensive Rating") + xlab("") + ylab("") + theme_classic() + theme(plot.title = element_text(hjust = 0.5)) + geom_text(aes(label=round(avg, 4)),position=position_dodge(width=0.9), vjust=-0.25) + scale_fill_manual(name = "Postseason", labels = c("No", "Yes"),values = c("#ADD8E6", "#E8ADAA"))


teamstats %>% ggplot(aes(W, Adjusted.DRtg.A)) + geom_point() + xlab("Wins") + ylab("Adjusted Defensive Rating") + ggtitle("Adjusted Defensive Rating vs. Wins") + theme_classic() + theme(plot.title = element_text(hjust = 0.5)) + geom_smooth(method="lm")

myreg <- lm(Adjusted.DRtg.A ~ W, data = teamstats)
summary(myreg)
```

# RESULTS
```{r}
playerstats <- read.csv("/Users/patricksimpson/Desktop/KmeansResults.csv")
```

## 2015-16:
```{r}
playerstats %>% group_by(fit.cluster) %>% filter(slugSeason == "2015-16") %>% summarise(vorp = mean(VORP), bpm = mean(BPM), dpm = mean(DBPM), opm = mean(OBPM))

playerstats %>% filter(fit.cluster == 11 & slugSeason == "2015-16") %>% select(namePlayer)
# Positive VORPS: 2,3,5,6,8, 
```

```{r}
playerstats %>% filter(slugSeason == "2015-16" & fit.cluster %in% c(2, 3, 5, 8, 11)) %>% group_by(fit.cluster) %>% summarise(pts = mean(PTS), rbd = mean(TRB), ast = mean(AST), sal = mean(Salary))


```

```{r}
#testbook <- read.csv("/Users/patricksimpson/Desktop/Testbook.csv")
testbook <- testbook %>% filter(Season == "2015-16")
testbook$clus1 <- as.factor(testbook$clus1)
testbook$clus2 <- as.factor(testbook$clus2)
testbook$clus3 <- as.factor(testbook$clus3)
testbook$clus4 <- as.factor(testbook$clus4)
testbook$clus5 <- as.factor(testbook$clus5)
testbook$clus8 <- as.factor(testbook$clus8)
testbook$clus11 <- as.factor(testbook$clus11)
testbook$Postseason <- as.factor(testbook$Postseason)


accept_rank <- glm(Postseason ~ clus8, data = testbook, family = "binomial")
summary(accept_rank)

```

## Clust 2
```{r}

post_2 <- glm(Postseason ~ clus2, data = testbook, family = "binomial")
summary(post_2)
predict(post_2, data.frame(clus2 = factor(c(1.0, 2.0, 3.0, 4.0, 5, 6, 7))), type = "response")
```

## Clust 3
```{r}
x3 <- lm(W ~ clus8, data = testbook)
summary(x3)
post_3 <- glm(Postseason ~ clus3, data = testbook, family = "binomial")
summary(post_3)
#predict(post_3, data.frame(clus3 = factor(c(1.0, 2.0))), type = "response")
```



```{r}
GPAAdmit <- ggplot(data = testbook, aes(x = clus8, y = Postseason)) +
  stat_smooth(method="glm",method.args=list(family="binomial"), se=FALSE)
print(GPAAdmit + 
        ggtitle("Admit Probability Given GPA") + 
        theme(plot.title = element_text(hjust = 0.5)) +
        labs (x = "GPA", y = "Admission Proability"))

xgre <- seq(0, 5, 0.01)

ygre <- predict(accept_rank, list(clus8 = xgre), type = "response")

plot(testbook$clus8, testbook$Postseason, pch = 16, xlab = "GRE score", ylab = "Admission Probability", main = "Admission Probability given GRE score", xlim = c(0,5))

lines(xgre, ygre)
abline(v=800, col="blue", lty = 5)


```