---
title: "SC"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(nbastatR)
```

# Function that returns three point shooting data for a player in a given season:
```{r}
dribdefense <- read.csv("/Users/patricksimpson/Desktop/NBAHC/dribdefense.csv")
shootingdata <- read.csv("/Users/patricksimpson/Desktop/NBAHC/Shooting/shootingdata.csv")

threepointshooting <- function(id, season){
  dribdefense <- dribdefense %>% filter(idPlayer == id & Season == season)
  tight <- dribdefense %>% filter(CloseDefDistRange != "4-6 Feet - Open" & CloseDefDistRange != "6+ Feet - Wide Open")
  open <- dribdefense %>% filter(CloseDefDistRange != "0-2 Feet - Very Tight" & CloseDefDistRange != "2-4 Feet - Tight" & CloseDefDistRange != "6+ Feet - Wide Open")
  wideopen <- dribdefense %>% filter(CloseDefDistRange != "0-2 Feet - Open" & CloseDefDistRange != "2-4 Feet - Tight" & CloseDefDistRange != "4-6 Feet - Open")
  
  tightattempts <- sum(tight$fg3a) # Tight Attempts
  tightmakes <- sum(tight$fg3m) # Tight Makes
  openattempts <- sum(open$fg3a) # Open Attempts
  openmakes <- sum(open$fg3m) # Open Makes
  wideopenattempts <- sum(wideopen$fg3a) # Wide Open Attempts
  wideopenmakes <- sum(wideopen$fg3m) # Wide Open Makes
  
  tightprop <- tightattempts / (tightattempts + openattempts + wideopenattempts) # Tight Proportion
  openprop <- openattempts / (tightattempts + openattempts + wideopenattempts) # Open Proportion
  wideopenprop <- wideopenattempts / (tightattempts + openattempts + wideopenattempts) # Wide Open Proportion
  
  tightpercentage <- tightmakes / tightattempts # Tight Percentage
  openpercentage <- openmakes / openattempts # Open Percentage
  wideopenpercentage <- wideopenmakes / wideopenattempts # Wide Open Percentage
  
  shootingdata <- shootingdata %>% filter(slugSeason == season & idPlayer == id & typeShot == "3PT Field Goal")
  atb <- shootingdata %>% filter(zoneBasic == "Above the Break 3")
  corner <- shootingdata %>% filter(zoneBasic != "Above the Break 3" & zoneBasic != "In The Paint (Non-RA)" & zoneBasic != "Mid-Range" & zoneBasic != "Restricted Area" & zoneBasic != "Backcourt")
  
  threeattempts <- nrow(shootingdata) # Total 3PT Attempts
  
  atbattempts <- nrow(atb) # ATB Attempts
  atbmakes <- sum(atb$typeEvent == "Made Shot") # ATB makes
  cornerattempts <- nrow(corner) # Corner Attempts
  cornermakes <- sum(corner$typeEvent == "Made Shot") # Corner Makes
  
  atbprop <- atbattempts / (atbattempts + cornerattempts) # ATB Proportion
  cornerprop <- cornerattempts / (atbattempts + cornerattempts) # Corner Proportion
  
  atbpercentage <- atbmakes / atbattempts # ATB Percentage
  cornerpercentage <- cornermakes / cornerattempts # Corner Percentage
  
  name <- idtoname(id) # Player name
  gp <- gamesplayed(id, season) # Games Played
  mp <- minutesplayed(id, season) # Minutes Played
  pos <- position(id, season) # Position Played
  fg3ag <- threeattempts / gp # 3 point attempts per game
  
  playerdf <- as.data.frame(cbind(name, id, season, pos, gp, mp, threeattempts, fg3ag, tightprop, openprop, wideopenprop, tightpercentage, openpercentage, wideopenpercentage, atbprop, cornerprop, atbpercentage, cornerpercentage))
  
  colnames(playerdf) <- c("namePlayer", "idPlayer", "Season", "position", "gamesPlayed", "minutesPlayed", "FG3A", "FG3AG", "tightProp", "openProp", "wideopenProp", "tight%", "open%", "wideopen%",
                      "atbProp", "cornerProp", "atb%", "corner%")
  return(playerdf)                    
}
```


# Creating Master 3 point shooting dataframe for 2018-19:
```{r}
myroster <- roster("2013-14")
for(i in 1:nrow(myroster)){
  id <- myroster[i,14]
  if(i == 1){
    shooting1314 <- threepointshooting(id, "2013-14")
  } else{
    helper <- threepointshooting(id, "2013-14")
    shooting1314 <- rbind(shooting1314, helper)
  }
  i = i + 1
}
remove(id, helper, myroster)

shooting <- rbind(shooting, shooting1718, shooting1617, shooting1516, shooting1415, shooting1314)
remove(shooting1718, shooting1617, shooting1516, shooting1415, shooting1314)

```

# Three point percentages based on defender proximity in a given season:
```{r}
openpercentage <- function(season){
  df <- dribdefense %>% filter(CloseDefDistRange != "0-2 Feet - Very Tight" & CloseDefDistRange != "2-4 Feet - Tight" & CloseDefDistRange != "6+ Feet - Wide Open" & Season == season)
  attempts <- sum(df$fg3a)
  makes <- sum(df$fg3m)
  percentage <- makes / attempts
  return(percentage)
}

wideopenpercentage <- function(season){
  df <- dribdefense %>% filter(CloseDefDistRange != "0-2 Feet - Very Tight" & CloseDefDistRange != "2-4 Feet - Tight" & CloseDefDistRange != "4-6 Feet - Open" & Season == season)
  attempts <- sum(df$fg3a)
  makes <- sum(df$fg3m)
  percentage <- makes / attempts
  return(percentage)
}

tightpercentage <- function(season){
  df <- dribdefense %>% filter(CloseDefDistRange != "6+ Feet - Wide Open" & CloseDefDistRange != "4-6 Feet - Open" & Season == season)
  attempts <- sum(df$fg3a)
  makes <- sum(df$fg3m)
  percentage <- makes / attempts
  return(percentage)
}
```

# Adding Shooting Rating Component
```{r}
shooting$Season <- as.character(shooting$Season)
for(i in 1:nrow(shooting)){
  id <- shooting[i,2]
  year <- shooting[i,3]
  component <- shooting[i,5]*(shooting[i,8]-tightpercentage(year)) + shooting[i,6]*(shooting[i,9]-openpercentage(year)) + shooting[i,7]*(shooting[i,10]-wideopenpercentage(year)) + shooting[i,11]*(shooting[i,13]-atb3percentage(year)) + shooting[i,12]*(shooting[i,14]-corner3percentage(year))
  if(i == 1){
    scomp <- as.data.frame(component)
  } else{
    help <- as.data.frame(component)
    scomp <- as.data.frame(rbind(scomp, help))
  }
  i = i + 1
}

rownames(scomp) <- c()
colnames(scomp) <- c("Component")
shooting <- cbind(shooting, scomp)

adjustedcomponent <- shooting %>% mutate(adjcomp = Component)

```

# Function to return position based on id and season:
```{r}
rosters <- read.csv("/Users/patricksimpson/Desktop/NBAHC/rosters.csv")
position <- function(id, season){
  df <- rosters %>% filter(slugSeason == season & idPlayer == id)
  position <- df[1,7]
  return(as.character(position))
}

```

# Adding position to DribDefense Data Frame:
```{r}
for(i in 1:nrow(dribdefense)){
  if(i == 1){
    pos <- as.data.frame(position(as.integer(dribdefense[i,12]), as.character(dribdefense[i,1])))
  } else{
    help <- as.data.frame(position(as.integer(dribdefense[i,12]), as.character(dribdefense[i,1])))
    pos <- as.data.frame(rbind(pos, help))
  }
  i = i + 1
}
colnames(pos) <- c("Position")
rownames(pos) <- c()
dribdefense <- cbind(dribdefense, pos)
remove(pos)
dribdefense <- dribdefense %>% select(Season:slugTeam, Position, idPlayer:frequencyFG3A)
```

# Adjusted Shooting Component
```{r}
shooting <- shooting %>% mutate(adjcom = ifelse(FG3AG <= .5 & gp >= 40, Component - 2, ifelse(gp <= 40 & FG3AG <= 2, Component - 2, ifelse(gp <= 25, Component - .25, ifelse(FG3AG = 0, Component - 3, Component + FG3AG / gp)))))


shooting <- shooting %>% mutate(adjcom = ifelse(FG3AG <= 1, Component - 2, ifelse(gp <= 25, Component - 2, ifelse(FG3AG <= 0, Component - 3, Component + FG3AG/gp))))

```

# Creating three point shooting dataframe for a given season:
```{r}
threeseason <- function(season){
  rosters <- read.csv("/Users/patricksimpson/Desktop/NBAHC/rosters.csv")
  rosterseason <- rosters %>% filter(slugSeason == season) # Roster for given season
  
  for(i in 1:nrow(rosterseason)){
    myid <- rosterseason[i,14] # Player id
    if(i == 1){
      masterdf <- threepointshooting(myid, season)
    } else{
      helper <- threepointshooting(myid, season)
      masterdf <- rbind(masterdf, helper)
    }
    i = i + 1
  }
  return(masterdf)
}
```

# Shooting Component Function
```{r}
shotcomp <- function(season, tightprop, openprop, wideopenprop, tight, open, wideopen, atbprop, cornerprop, atb, corner){
  
  tightleague <- tightpercentage(season)
  openleague <- openpercentage(season)
  wideopenleague <- wideopenpercentage(season)
  atbleague <- atb3percentage(season)
  cornerleague <- corner3percentage(season)
  
  component <- tightprop *(tight - tightleague) + openprop * (open - openleague) + wideopenprop *(wideopen - wideopenleague) + atbprop * (atb - atbleague) + cornerprop * (corner - cornerleague)
  
  return(component)
}

```

# Getting shooting component (unadjusted) for each player:
```{r}
master$Season <- as.character(master$Season)

for(i in 1:nrow(master)){
  if(i == 1){
    comp_unadjust <- as.data.frame(shotcomp(master[i,3], master[i,9], master[i,10], master[i,11], master[i,12], master[i,13], master[i,14], master[i,15], master[i,16], master[i,17], master[i,18]))
  } else{
    helper <- as.data.frame(shotcomp(master[i,3], master[i,9], master[i,10], master[i,11], master[i,12], master[i,13], master[i,14], master[i,15], master[i,16], master[i,17], master[i,18]))
    comp_unadjust <- rbind(comp_unadjust, helper)
  }
  i = i + 1
}
remove(helper)
colnames(comp_unadjust) <- c("comp_unadjust")
master <- cbind(master, comp_unadjust)
```

# Scaling by FG3A:
```{r}
x <- as.data.frame(scale(master$FG3A))
master <- master %>% mutate(scaledfg = scale(FG3A)) %>% mutate(multiplier = exp(scaledfg) / ((exp(scaledfg)+1))) %>% mutate(comp_adjusted = comp_unadjust*multiplier^3) %>% mutate(adjustment = ifelse(comp_unadjust > 0, comp_unadjust*multiplier, comp_unadjust + abs(comp_unadjust*multiplier)))

# Filter out games played less than 10, fieldgoal attempts per game less than 1
```

